Appendix

### 2014-10-02 Rmarkdown/appendix.Rmd
Further work on Eckhardt et al.
Some analysis of Lacey (2013).

>>>>

__TODO: What is the general restriction on $c$ when $p_{h, i} \neq p_{h', i'}$?__

## Analysis of \cite{Lacey:2013iy}

I want to estimate the number of CpGs used by \cite{Lacey:2013iy} to estimate the correlation of methylation levels. They used the chromosome 11 data from an RRBS experiment on a normal myotube cell line, MTCTL2. Unfortunately, the data are not publicly available. Instead, I use data from ENCODE of a skeletal muscle myotubes cell line that had RRBS performed in triplicate (HSMMtube).

Firstly, I download the data and unzip it:
```{r, cache = TRUE, message = FALSE}
library(R.utils)
library(data.table)
library(dplyr)

tmp <- tempdir()
url <- 'http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeHaibMethylRrbs/'
files <- paste0(url, 'wgEncodeHaibMethylRrbsHsmmtubefshdDukeSitesRep', 
                     1:3, '.bed.gz')
dests <- paste0(tmp,'/rep', 1:3, '.bed.gz')
x <- mapply(function(f, d) {
  download.file(f, d)
  gunzip(filename = d, overwrite = TRUE)
  fread(gsub(pattern = '.gz', replacement = '', x = d), sep = '\t')
  }, files, dests, SIMPLIFY = FALSE)
```

Then I count the number of CpGs on chromosome 11 in each sample:
```{r}
y <- lapply(x, function(xx) {
  xx <- tbl_dt(xx)
  xx %>% 
    group_by(V1) %>% 
    summarise(n())
})

rbind_all(y) %>% filter(V1 == 'chr11')
```

### TODOs

* Cite data source and publication
